---
title: "Lab 9"
author: "Pablo Nguyen"
format:
  html:
    fig-cap-location: top
    theme: cerulean
    self-contained: true
    code-overflow: wrap
    code-tools: true
    code-fold: true
execute: 
  echo: true
  errors: true
  warning: false
---
Setup
```{r setup}
library(tidyverse)
library(moderndive)
library(skimr)
library(gapminder)
library(broom)
library(janitor)
library(gt)
StateNames_A <- read_csv(here::here("week9", "labs", 
                                    "BabyNames", "StateNames_A.csv")) 

```
3.1
```{r Make Table}

StateNames_A <- StateNames_A %>%
  rename("Sex" = "Gender")
  
Allison_stats <- StateNames_A |>
  filter(Name == "Allison") |>
  group_by(State, Sex) |>
  summarize(count_total = sum(Count), .groups = "drop") |> 
  pivot_wider(names_from = Sex, values_from = count_total, values_fill = 0) 
Allison_stats

```
3.2
```{r only females}
allison_f <- StateNames_A |>
  filter(Sex == "F", Name == "Allison" ) 
```
3.3
```{r create vis}
count_by_year <- allison_f |>
  group_by(Year) |>
  summarize(total_count = sum(Count), .groups = "drop") 


ggplot(data = count_by_year, mapping = aes(x = Year, y = total_count)) +
  geom_point() + 
  labs(y = NULL, title = "Total Number of Allisons Born by Year",
       x = "Year")
```
4.4
```{r create regression}
linear_model <- lm(total_count ~ Year, data = count_by_year)
```
4.5
The Linear Model is :
Estimated Total Number of Allisons = 209690 - 102*Year
 
4.6 
```{r residuals}
linear_model |>
  broom::augment() |>
  ggplot(mapping = aes(y = .resid, x = .fitted)) +
  geom_point() +
  labs(title = "Residuals by Fitted Values", y = NULL, x = "Fitted Values")
```
When observing Residuals by Fitted Values, We can see that equivariance is not satisfied. Residuals are higher near the extreme values and lower near the middle values of the study. Therefore, We might consider using log(x) values.

4.7
According to the Model, the Name Allison is not very cool anymore since the year coefficient is negative. Therefore, as the years go on, Allison gets less popular.


5.8
```{r similar names}
Allen_names <- StateNames_A |> 
  filter(Name %in% c("Allen", "Allan", "Alan"))

Allen_names |>
  group_by(Year, Name) |>
  summarize(Yearly_Count = sum(Count), .groups = "drop") |>
  ggplot(mapping = aes(x = Year, y = Yearly_Count, color = Name)) +
           geom_line()
```

5.9
```{r CA vs PA}
#Filter Allen names by CA and PA state name
Allen_names_CA_PA <- Allen_names |>
  filter(State == "CA" | State == "PA") |>
  group_by(State, Name) |>
  summarize(Total_Count = sum(Count, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(names_from = Name, values_from = Total_Count, values_fill = 0) 
  
Allen_names_CA_PA
```

5.10
```{r Ratios}
Allen_names_CA_PA |>
  #Find the sum of each Row
  mutate(Total = pmap_int(list(Alan, Allan, Allen), sum)) |>
  #find ratio by dividing each count by the total count of each row
  mutate(
    across(.cols = c(Alan:Allen), 
           ~ .x/Total)
    ) |>
  subset(select = -c(Total))
#got some help from this website:
#https://stackoverflow.com/questions/
#21818181/applying-a-function-to-every-row-of-a-table-using-dplyr
```
We can see Tha Pennsylvania Uses the 'Allen' spelling significantly more than California, while California uses the 'Alan' Spelling more the Pennsylvania.