---
title: "pa 9.2"
author: "Pablo Nguyen"
format:
  html:
    fig-cap-location: top
    theme: cerulean
    self-contained: true
    code-overflow: wrap
    code-tools: true
    code-fold: true
execute: 
  echo: true
  errors: true
  warning: false
---
```{r}
library(tidyverse)
library(moderndive)
library(skimr)
library(gapminder)
library(broom)
library(janitor)
```


Trombones weights are Normally distributed, with a mean weight of 4.6 pounds and a standard deviation of 0.8 pounds.

Trumpet weights are Uniformly distributed between 1.5 and 3.5 pounds.

Reed instruments (like clarinets, bassoons, and saxophones) have weights that are Chi-Square distributed with 4 degrees of freedom.

```{r warm up}
qunif(p = .95, min = 1.5, max = 3.5)
qnorm(.10, mean = 4.6, sd = .8)
1-pnorm(q = 5, mean = 4.6, sd = .8)
1-pchisq(q = 5, df = 4)
sum(rnorm(n = 100, mean = 4.6, sd = .8)<4)
```

2 Warm-up
What is the 95th percentile for trumpet weight?
3.4
What is the 10th percentile for trombone weight?
3.574
About what percent of trombones do you expect to be more than 5 pounds?
.3085, or 30.85%
About what percent of reed instruments do you expect to be more than 5 pounds?
.2872, or 28,72%
Simulate 100 random trombone weights. How many of them were below 4 pounds?
19 - 31


3 Catching a Con
You manage to intercept a shipping notice for delivery to Professor Hill. It says the following:

Wells Fargo Shipment 1957

To:  Harold Hill, Mason City, Iowa
From:  Music Factory, Gary, Indiana

Items included:
    Trombones: 76
    Cornets: 110
    Saxophones: 542
    Clarinets: 318
    Bassoons: 175
    
Total Shipped Weight: 4532 lbs.
This is your chance to catch Professor Hill in his lie!

First, write a function that samples the correct number of weights of trombones, cornets (trumpets), and reed instruments (saxophones, clarinets, bassoons), and then returns the total weight of the shipment.

Then, use that function to create random samples of the total weight of 1000 possible shipments.

```{r function}
set.seed(1957)

music_man <- function(n_tromb, n_cor, n_reed){
  
  trombones <- sum(rnorm(n_tromb, mean = 4.6, sd = .8))
  cornets <- sum(runif(n_cor, min = 1.5, max = 3.5))
  reeds <- sum(rchisq(n_reed, df = 4))
  
  return(trombones + cornets + reeds)
  
}

my_weights <- map_dbl(.x = 1:1000, 
                      .f = ~ music_man(n_tromb = 76, n_cor = 110, n_reed = 1035)
                      ) 
sum(my_weights <= 4532)
```

Only 7 were below the number, I think he is lying